% resume.tex
% vim:set ft=tex spell:

\documentclass[10pt,a4paper,hidelinks]{article}
\usepackage[a4paper,margin=0.75in]{geometry}
\usepackage{mdwlist}
\usepackage{textcomp}
\usepackage{tgpagella}
\usepackage{hyperref}
\usepackage{setspace}
\usepackage{enumitem}
\usepackage{fontawesome}

% Font stuff %

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\pagestyle{empty}
% fontawesome external link
% {\textsuperscript{\faExternalLink}}
    
% \RequirePackage[quiet]{fontspec}
% \RequirePackage[math-style=TeX]{unicode-math}

% \defaultfontfeatures{Mapping=tex-text}

% \setmainfont
% [Path = fonts/, Mapping=tex-text, Color=textcolor,
% BoldFont=texgyreheros-bold.otf,
% ItalicFont=texgyreheros-italic.otf,
% BoldItalicFont=texgyreheros-bolditalic.otf
% ]
% {texgyreheros-regular.otf}

% \setmathfont{texgyreheros-regular.otf}

% \setlength{\tabcolsep}{0em}

 % -------------------------*--------------------------- %


% indent section style, used for sections that aren't already in lists
% that need indentation to the level of all text in the document
\newenvironment{indentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{#1}}%
	\item[]%
}
{\end{list}}

% opposite of above; bump a section back toward the left margin
\newenvironment{unindentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{-0.5#1}}%
	\item[]%
}
{\end{list}}

% format two pieces of text, one left aligned and one right aligned
\newcommand{\headerrow}[2]
{\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
	#1 &
	#2 \\
\end{tabular*}}

% and the actual content starts here
\begin{document}

\begin{center}
\setstretch{1.2}{
{\huge \textbf{Rudra Narayan Kar}}

{\large{Software Engineer}} \\

+91 8763701890\ \ \textbullet
\ \ kar.rudra008@gmail.com 

\href{https://mrprofessor.io}{mrprofessor.io} \ \ \textbullet
\ \ \href{https://github.com/mrprofessor}{github.com/mrprofessor} \ \textbullet
\ \ \href{https://linkedin.com/in/mrprofessor}{linkedin.com/in/mrprofessor}
\\
}
\end{center}


\hrule
\vspace{-0.4em}
\section*{Experience}

% First list shouldn't have any bullet/dash and the second
% iterative list should have bullet
\renewcommand{\labelitemi}{$\bullet$}
% \renewcommand\labelitemii{$\--$}

\begin{itemize}
    \setlength\itemsep{5pt}
	\parskip=0.1em

	\item
	\headerrow
		{\textbf{Software Development Engineer}}
		{\href{https://www.turbot.com/}{\textbf{Turbot, Kolkata}}}
	\\
	\headerrow
	    {\emph{Jan 2018 -- Present}}
		{\emph{}}
	\begin{itemize*}
	   % \setlength\itemsep{2pt}
		\item Currently working as a member of core UI team \& responsible for building various modular and reusable components using React.
        \item Architected the integration of \textbf{AWS Inspector} service which helped Turbot become a featured partner of \href{https://aws.amazon.com/inspector/partners/}{\textbf{Inspector}}.
        \item Made Turbot Azure \textbf{CIS} compliant by implementing most of the CIS Microsoft Azure Foundations Benchmark v1.0.0.
        \item Added object level access control restrictions for \textbf{Google Cloud Platform} storage service by building a custom inventory.
        \item Fixed a number of bugs (both back-end \& UI) while working closely with the customer support team.
        \item Current webmaster of the official website of the company.
	\end{itemize*}

	\item
	\headerrow
		{\textbf{UI Developer}}
		{\href{https://www.topcoder.com/}{\textbf{Topgear, Wipro, Chennai}}}
	\\
	\headerrow
	    {\emph{Nov 2016 -- Dec 2017}}
		{\emph{}}
	\begin{itemize*}
	   % \setlength\itemsep{2pt}
		\item Made the case for moving to \textbf{React + Redux} \& successfully ported the employee exit portal from angularJs to \textbf{React}.
        \item Developed the aircraft data management portal of a client using React.
        \item Wrote a huge amount of wikis for Python \& UI/UX development community.
	\end{itemize*}

	\item
	\headerrow
		{\textbf{Project Engineer}}
		{\href{https://www.wipro.com/en-IN/product-engineering/}{\textbf{Product Engineering Services, Wipro, Chennai}}}
	\\
	\headerrow
		{\emph{Jul 2016 -- Dec 2017}}
		{\emph{}}
	\begin{itemize*}
	   % \setlength\itemsep{2pt}
		\item In a team of four, developed an IDE for a legacy Domain Specific Language.
        \item Implemented \textbf{Syntax highlighting} \& \textbf{Intellisense} using Xtext framework on the same.
        \item Customized most of the Mantis bug tracker as per the project requirement \& maintained it for the most part of my tenure.
        \item Topper of \textbf{Wipro CodeExpress 2016} ( Product Engineering Services ) \& Digithon ( Wipro Digital ).
	\end{itemize*}

%     \item
% 	\headerrow
% 		{\textbf{Freelance Web Developer}}
% 		{\textbf{Bhubaneswar, Odisha}}
% 	\\
% 	\headerrow
% 		{\emph{Dec 2013 -- May 2016}}
% 		{\emph{}}
% 	\begin{itemize*}
% 	   % \setlength\itemsep{2pt}
%         \item Designed, developed \& maintained the website of an event management company for three years.
%         \item Developed \& deployed an WordPress site for a local business.
%         % \item Designed the college cult-fest website for two years.
% 	\end{itemize*}
	
\end{itemize}


\hrule
\vspace{-0.4em}
\section*{Education}

\begin{itemize}
	\parskip=0.1em

	\item 
	\headerrow
		{\textbf{B.Tech In Computer Science \& Engineering}}
		{{\href{http://www.bput.ac.in/}{\textbf{BPUT, Odisha}}}}
	\\
	\headerrow
		{\emph{Jul 2012 -- Jun 2016}}
		{\emph{}}
	\begin{itemize*}
	   % \setlength\itemsep{2pt}
		\item {Algorithms, Data Structures, Complexity Analysis, Compiler Design, OOP, Networking, Operating Systems, Computer Architecture, C/Python.}
	\end{itemize*}

\end{itemize}


\hrule
\vspace{-0.4em}
\section*{Certifications}

\begin{itemize}
	\parskip=0.1em

	\item 
	\headerrow
		{\textbf{Red Hat Certified System Administrator}}
		{{\href{https://www.redhat.com/}{\textbf{Red Hat}}}}
	\\
	\headerrow
	    {\emph{\href{https://www.redhat.com/rhtapps/certification/verify/?certId=150-141-034}{www.redhat.com/rhtapps/certification/verify/?certId=150-141-034}}}
		{\emph{}}
	
	\item 
	\headerrow
		{\textbf{Microsoft AZURE214x}}
		{{\href{https://www.microsoft.com/}{\textbf{Microsoft}}}}
	\\
	\headerrow
	    {\emph{\href{https://openedx.microsoft.com/certificates/f0864cf4e5414a4387c0b6b1e5dcd880}{openedx.microsoft.com/certificates/f0864cf4e5414a4387c0b6b1e5dcd880}}}
		{\emph{}}

\end{itemize}


\hrule
\vspace{-0.4em}
\section*{Technical Skills}

\begin{indentsection}{\parindent}
\hyphenpenalty=1000
\begin{description*}
	\item[Strong:]
	JavaScript, React, Express, Serverless, RESTful architecture, Git, AWS
	\item[Knowledgeable:]
	Graphql, Redux, Python, GCP, Azure, MongoDB
\end{description*}
\end{indentsection}

\end{document}
